Verification of Stencil Computations through Spatial Specifications

### 2016-07-07 paper.tex
Minor fortran typo

The sum of two regions $r \texttt{+} r'$ specifies that an array is
read using the neighbourhood indices described by either $r$ or
$r'$; it acts as a disjunction on specifications. For
example, the following gives the specification of a five-point
stencil which is the sum of two compound \texttt{reflexive} and
\texttt{centered} regions in each dimension:
%%
\begin{minted}{fortran}
!= stencil centered(depth=1, dim=1)*reflexive(dim=2) + centered(depth=1, dim=2)*reflexive(dim=1) :: a
b(i,j) = -4*a(i,j) + a(i-1,j) + a(i+1,j)
                   + a(i,j-1) + a(i,j+1)
\end{minted}
%%
Here the left-hand side of \texttt{+} says that when the second dimension
(induction variable $j$) is fixed at the origin, the first dimension
(induction variable $i$) accesses the immediate vicinity of the origin
(to depth of one). The right hand side of \texttt{+} is similar but the dimensions are reversed.
This reflects the symmetry under rotation of the five-point stencil.

>>>>

The sum of two regions $r \texttt{+} r'$ specifies that an array is
read using the neighbourhood indices described by either $r$ or
$r'$; it acts as a disjunction on specifications. For
example, the following gives the specification of a five-point
stencil which is the sum of two compound \texttt{reflexive} and
\texttt{centered} regions in each dimension:
%%
\begin{minted}{fortran}
!= stencil centered(depth=1, dim=1)*reflexive(dim=2) + centered(depth=1, dim=2)*reflexive(dim=1) :: a
b(i,j) = -4*a(i,j) + a(i-1,j) + a(i+1,j) &
                   + a(i,j-1) + a(i,j+1)
\end{minted}
%%
Here the left-hand side of \texttt{+} says that when the second dimension
(induction variable $j$) is fixed at the origin, the first dimension
(induction variable $i$) accesses the immediate vicinity of the origin
(to depth of one). The right hand side of \texttt{+} is similar but the dimensions are reversed.
This reflects the symmetry under rotation of the five-point stencil.
